---
main_topsize: 0.1 #percent coverage of the poster
main_bottomsize: 0.09
#ESSENTIALS
# title: '**Feedforward Neural Networks as Statistical Models**'
poster_height: "46.8in"
poster_width: "33.1in"
main_textsize: "78pt"
author_textsize: "72pt"
affiliation_textsize: "36pt"
twitter_textsize: "50pt"
email_textsize: "50pt"
sup_textsize: "32pt"
body_textsize: "36pt"
main_img_left_bottom: "0.0in"
main_img_left_left: "0.0in"
main_img_left_width: "70%"
primary_colour: "#203864"
secondary_colour: "#203864"
accent_colour: "#0099ff"
author:
  - name: '**Andrew McInerney**'
    affil: 1
    main: true
    twitter: amcinerney_
    github: andrew-mcinerney
    email: andrew.mcinerney@ul.ie
  - name: Kevin Burke
    affil: 1
    main: true
affiliation:
  - num: 1
    address: Department of Mathematics & Statistics, University of Limerick
main_findings:
  - "**statnn**: Feedforward **neural networks** as **statistical models**"
logoleft_name: figures/bottom-banner.png
logoright_name: figures/logo.png
# logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  tidy = FALSE,
  message = FALSE,
  fig.align = "center",
  out.width = "100%"
)
options(knitr.table.format = "html")
```

```{r stnn, cache = TRUE}
library(statnn)
library(caret)
library(nnet)
std <- caret::preProcess(Boston)

X <- predict(std, Boston)[, -ncol(Boston)]
std_y <- caret::preProcess(data.frame("medv" = Boston[, ncol(Boston)]))
y <- as.matrix(predict(std_y, data.frame("medv" = Boston[, ncol(Boston)])))

set.seed(100)
nn <- nnet(X, y,
  size = 2, trace = FALSE,
  linout = TRUE, maxit = 1000
)

stnn <- statnn(nn, X = X)
```


# Introduction

Currently, there are around 80 packages available on the Comprehensive R Archive Network (CRAN) that allow for the fitting of neural networks.
Some of the more popular packages are **nnet** [@nnet], **neuralnet** [@neuralnet], **keras** [@keras], and **torch** [@torch].
The goal of our R package, \textbf{statnn}, is to extend some of the existing R packages for neural networks to allow for more useful and insightful statistical-based methods and outputs.
This not only increases the utility of neural networks for statisticians, but it also bridges the gap between the explainability and flexibility of neural networks.
This package, to the best of our knowledge, is the first package in R that provides these statistically-based summaries for neural networks.


# Installation
You can install the development version of **statnn** from [GitHub](https://github.com/) with:

```{r, echo = TRUE, eval = FALSE}
# install.packages("devtools")
devtools::install_github(
  "andrew-mcinerney/statnn"
  )
```

# Implementation

The use of **statnn** is explained through a real-data application.
Here, we use the Boston Housing dataset, and we use the **nnet** function for fitting our neural network.

```{r, eval = FALSE, echo = TRUE}
library(statnn)
# set.seed(100)
nn <- nn_fit(
  formula = medv ~ ., data = Boston,
  q = 2, n_init = 10, pkg = "nnet"
)
```


We can then convert the fitted neural network to an object of class `"statnn"` using 

```{r, eval = FALSE, echo = TRUE}
stnn <- statnn(nn)
```

# Model Summary

The `summary()` method can then be used on the new object, `stnn`, to get a useful, statistical-based summary table for the neural network, similar to that of other regression models in R.

```{r, echo = TRUE, eval = FALSE}
summary(stnn)
```

```{r}
library(statnn)
cat(c("[...]", capture.output(summary(stnn))[9:24],
      gsub('(.{1,52})(\\s|$)', '\\1\n',  capture.output(summary(stnn))[25]),
      "[...]")
    , sep = "\n")
```

The `plotnn()` function is used to visualise results of the single- and multiple-parameter Wald tests in a diagram of the neural network architecture.
The significance level can be changed using the `alpha` argument (default: 0.05).
By default, significant weights and nodes are coloured black and insignificant weights and nodes are coloured light grey.
The intercept terms can be displayed by setting `intercept = TRUE` (default: `FALSE`).

```{r, echo = TRUE}
plotnn(stnn)
```

The `plotci()` function is used to visualise the Wald (1 - $\alpha$)100\% single-parameter confidence intervals and the Wald (1 - $\alpha$)100\% joint confidence ellipses for the input-to-hidden-layer weights for each covariate.
The `which` argument specifies which covariate's confidence intervals are to be displayed (default: `NULL`, displays plots for all covariates).

```{r, echo = TRUE}
plotci(stnn, which = 7)
```

# Covariate Effect Plots

# References
